Estimating the incidence of SARS-CoV-2 from prevalence data

### 2023-06-09 cis-imperfect-testing.tex
Bit of editing and organising

\begin{figure}
  \centering %\includegraphic{}
  \todo[inline]{Figure showing estimates without false negatives}
  \caption{\label{imperf-test:fig:problem-cis-estimates}}
\end{figure}

@@

Examination of the CIS data also provides evidence for a declining test sensitivity.
We can approximately bound the test sensitivity by assuming that all intermittent negatives are false negatives, that the negative following the last positive in an episode could be either a true or false negative, and all other negatives are true negatives.
The point estimate for the test sensitivity is the true positives / (true positives + false negatives).
In \cref{imperf-test:fig:bounding-cis-sensitivity} we consider the values produced by assuming the negative following the last positive in an episode could be either a true or false negative as a function of time since the individual was detected (\ie: the first positive test in the episode).
While the bounds are broad, they clearly suggest a declining test sensitivity over the course of an episode.
\begin{figure}
  \todo[inline]{Include the analysis of CIS data with bounding test sensitivity}
  \caption{Bounding the test sensitivity using CIS data as a function of time since the infection was detected (see main text for explanation of how the bounds are formed).\label{imperf-test:fig:bounding-cis-sensitivity}}
\end{figure}

>>>>

\begin{figure}
  \centering %\includegraphic{}
  \todo[inline]{Figure showing estimates without false negatives}
  \caption[Estimating survival using CIS data assuming perfect testing]{Estimating the survival function using CIS data and the model of \cref{perf-test} gives implausibly short estimates. \label{imperf-test:fig:problem-cis-estimates}}
\end{figure}

@@

Examination of the CIS data also provides evidence for a declining test sensitivity.
We can approximately bound the test sensitivity by assuming that all intermittent negatives are false negatives, that the negative following the last positive in an episode could be either a true or false negative, and all other negatives are true negatives.
The point estimate for the test sensitivity is the true positives / (true positives + false negatives).
In \cref{imperf-test:fig:bounding-cis-sensitivity} we consider the values produced by assuming the negative following the last positive in an episode could be either a true or false negative as a function of time since the individual was detected (\ie: the first positive test in the episode).
While the bounds are broad, they clearly suggest a declining test sensitivity over the course of an episode.
\begin{figure}
  \todo[inline]{Include the analysis of CIS data with bounding test sensitivity}
  \caption[Bounding test sensitivity using CIS data]{Bounding the test sensitivity using CIS data as a function of time since the infection was detected (see main text for explanation of how the bounds are formed).\label{imperf-test:fig:bounding-cis-sensitivity}}
\end{figure}

### 2023-06-09 thesis.tex
Bit of editing and organising

@@

@@

@@

\chapter{Text to use}

Random bits of text that I've written that don't currently fit anywhere but will likely be useful in future

\section{CIS study description}
The CIS continually enrols individuals and tests them on an ongoing basis, following a
specified testing protocol. The protocol specifies that the initial five
tests are spaced every 7 days, then the spacing is every 28 days.
However, real-world considerations often lead to variations in test
times and missed tests. Our analysis focuses solely on the binary result
(positive or negative) of these tests, assuming no misclassification
bias.

>>>>

\chapter{Introduction} \label{intro}

\section{The COVID-19 pandemic and ongoing burden}

\section{SARS-CoV-2 and COVID-19}

\section{PCR testing} \label{intro:sec:PCR}

\section{Incidence, prevalence, and duration}

\section{Studies used in this thesis} \label{intro:sec:studies}

\subsection{Assessment of Transmission and Contagiousness of COVID-19 in Contacts}

\subsection{Coronavirus (COVID-19) Infection Survey} \label{intro:sec:cis}

The CIS (Coronavirus (COVID-19) Infection Survey) continually enrols individuals and tests them on an ongoing basis, following a
specified testing protocol. The protocol specifies that the initial five
tests are spaced every 7 days, then the spacing is every 28 days.
However, real-world considerations often lead to variations in test
times and missed tests. Our analysis focuses solely on the binary result
(positive or negative) of these tests, assuming no misclassification
bias.

\section{Thesis outline}

@@

\section{Background}

\section{Original analysis}

\section{Comparison to \texorpdfstring{\textcite{hakkiOnset}}{Hakki \etal (2022)}}

\section{Final analysis}

@@

\chapter{Statistical backcalculation}

\chapter{Mechanistic modelling}

\chapter{Conclusion}

@@
